---
title: "Hackathon - Task 1.4"
author: "Gayatri Shejwal"
date: "2023-12-18"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
pacman::p_load(gt, gtExtras, tidyverse, haven)
```

## 1.4 Perceived hatefulness of social media post

Create a gt/gtExtras table that reports the aggregated perceived hatefulness of a set of social media posts, following good practice of visualization. For this task, consider the following:

• Some guidance for the data preparation:

o The content of the social media posts is stored in two types of variables: vig\_{x}\*topic and vig*{x}*sender_message. Every respondent evaluated 8 different messages, which is why x goes from 1 to 8. The perception of hatefulness is stored in the variables vig*{x}\_hateful.

o Drop observations where vig_1_hateful is missing.

o Recode the vig\_{x}\_topic variables according to the following scheme: gender = "Women", ideologydems = "Democrats", ideologyreps = "Republicans", muslim = "Muslim immigrants".

o Construct the full content of the message by pasting together the strings of the recoded vig\_{x}*topic and vig*{x}\_sender_message variables. For instance, one of the full messages reads: "Republicans should be stopped from spreading falsehoods."

o For the evaluation, you should average across all evaluated vignettes across all responses, i.e. your unit of analysis is vignettes, not respondents.

• Your table should contain the following information: (1) The message text, (2) the mean and standard deviation of the hatefulness rating by message, and (3) a barplot displaying the distribution of hatefulness ratings 1 to 5 per message.

• The average hatefulness column should be colored by value.

• The table should provide a meaningful title and description, making it a standalone product that speaks for itself.

```{r}

# Load the survey and tracking datasets:
survey_df <- readRDS("survey/meof_usa_survey_df.RDS")

# Select the desired variables:
hate_df <- survey_df |>
  select(vig_1_topic, vig_2_topic, vig_3_topic, vig_4_topic,
         vig_5_topic, vig_6_topic, vig_7_topic, vig_8_topic,
         vig_1_sender_message, vig_2_sender_message,
         vig_3_sender_message, vig_4_sender_message,
         vig_5_sender_message, vig_6_sender_message,
         vig_7_sender_message, vig_8_sender_message,
         vig_1_hateful, vig_2_hateful,
         vig_3_hateful, vig_4_hateful,
         vig_5_hateful, vig_6_hateful,
         vig_7_hateful, vig_8_hateful) |>
  filter(!is.na(vig_1_hateful))


# Recoding the observations according to the guidelines:

hate_df <- hate_df |>
  mutate_at(vars(vig_1_topic:vig_8_topic),
            funs(recode(., "gender" = "Women", "ideologydems" = "Democrats", "ideologyreps" = "Republicans", "muslim" = "Muslim immigrants")))

# Construct the full content of the message:

hate_df <- hate_df |>
  mutate(vig_1_text = paste0(vig_1_topic, " " , vig_1_sender_message),
         vig_2_text = paste0(vig_2_topic, " " , vig_2_sender_message),
         vig_3_text = paste0(vig_3_topic, " " , vig_3_sender_message),
         vig_4_text = paste0(vig_4_topic, " " , vig_4_sender_message),
         vig_5_text = paste0(vig_5_topic, " " , vig_5_sender_message),
         vig_6_text = paste0(vig_6_topic, " " , vig_6_sender_message),
         vig_7_text = paste0(vig_7_topic, " " , vig_7_sender_message),
         vig_8_text = paste0(vig_8_topic, " " , vig_8_sender_message),
         )

# Filter the desired columns:
perceived_hate <- hate_df |>
  select(vig_1_text:vig_8_text, vig_1_hateful:vig_8_hateful)


# Pivot the table longer to stack the messages :
perceived_hate <- perceived_hate |>
  pivot_longer(c("vig_1_text":"vig_8_text"),
               names_to = "vig_text",
               values_to = "text_message") |>
  pivot_longer(c("vig_1_hateful":"vig_8_hateful"),
               names_to = "vig_hateful",
               values_to = "hateful_level") |>
  select(text_message, hateful_level)


table_1 <- perceived_hate |>
  group_by(text_message) |>
  summarise(avg_rating = mean(hateful_level, na.rm = TRUE),
            std_dev = sd(hateful_level, na.rm = TRUE),
            all_ratings = list(hateful_level), .groups = "drop") |>
  arrange(desc(avg_rating))

gt_table <- table_1 |>
  gt() |>
  tab_header(
    title = html("<strong>Aggregated Perceived Hatefulness of Social Media Posts</strong>"),
    subtitle = "This table shows how people perceive specific messages in the context of social media posts. The messages are displayed on a perception scale of 1 to 5: 1 being perceived as the least hateful and 5 as the most hateful by the surveyed population.") |>
  tab_options(column_labels.background.color = "lightgrey",
  source_notes.background.color = "lightgrey",
  source_notes.font.size = 10) |>
  tab_spanner(label = "Summary of Hatefulness Ratings", c(avg_rating, std_dev, all_ratings), replace = FALSE) |>
  cols_label(text_message = md("**Message**"), avg_rating = md("**Mean**"), std_dev = md("**Standard Deviation**"), all_ratings = md("**Distribution of All Ratings**")) |>
  fmt_number(columns = c(avg_rating, std_dev), decimals = 2) |>
  gt_hulk_col_numeric(avg_rating) |>
  gt_plt_dist(all_ratings, type = "histogram", line_color = "darkred",
  fill_color = "darkred", fig_dim = c(5,10), bw = 0.5) |>
  tab_source_note(source_note = "Source: Guess, Andrew M.; Barberá, Pablo; Yang, JungHwan; Munzert, Simon (2022): Media Exposure and Opinion Formation in an Age of Information Overload (MEOF) – Survey U.S.A. GESIS Data Archive, Cologne. ZA7895 Data file Version 1.0.0, doi:10.4232/1.13980.")

# Print the table:
gt_table


```
